---
title: "R Notebook for EU Analysis Data Project - Chukwuma Ofoegbu S211235"
output: html_notebook
---
```{r}
# Inactivity Rate:is the percentage of inactive persons in relation to the comparable total population.Inactive persons meaning persons part of the Labour force
# but are not employed/working.
# Inactivity Rate = 100 - Activity Rate
#(Activity rate is the percentage of active persons in relation to the comparable total population.)
```

```{r}
library(ggplot2)
library(regions)  # to process Regional Statistics (NUTS )
library(eurostat) # access to the Eurostat resources
#library(tibbletime)
library(dplyr)
library(tidyverse)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
# Step 2 - Download the data (directly from Eurostat, using eurostat library)
activity_rate_eu <- get_eurostat("lfst_r_lfp2actrtn", time_format = "num")
ls(activity_rate_eu)
unique(activity_rate_eu$unit)
unique(activity_rate_eu$geo)
unique(activity_rate_eu$isced11)
unique(activity_rate_eu$sex)
unique(activity_rate_eu$time)
unique(activity_rate_eu$citizen)
unique(activity_rate_eu$age)
```
```{r}
# Step 3 - Clean and filter the data  (Female inactivity rate aged 25-54)

activity_rate_eu <- activity_rate_eu %>%                        
  mutate(    edu = 
               case_when(
                 isced11 == "ED0-2" ~ "edu_low",
                 isced11 == "ED3_4" ~ "edu_medium",
                 isced11 == "ED5-8" ~ "edu_high",
                 isced11 == "NRP" ~ "NRP",
                 isced11 == "TOTAL" ~ "edu_total"
               )
  ) %>% 
  select(geo, unit, age, sex, edu, time, values, citizen)

# The inactivity rate is gotten as
inactivity_rate_eu <- activity_rate_eu
inactivity_rate_eu$values <- 100 - inactivity_rate_eu$values

```

```{r}
# First 5 rows of the activity rate
head(activity_rate_eu, 5)

# First 5 rows of the inactivity rate
head(inactivity_rate_eu, 5)
```


```{r}
# Filtering Regions for NUTS 2 and NUTS 0
library(regions)
eu_region <- nuts_changes
ls(eu_region)
names(eu_region) 
unique(eu_region$typology)


eu_region_2 <- nuts_changes %>%                 #nuts_changes - European Union: Recoded NUTS units 1995-2021
  filter(typology== "nuts_level_2") %>% 
  select(typology, code_2016, geo_name_2016) %>%
  drop_na()

eu_region_0 <- nuts_changes %>%                 #nuts_changes - European Union: Recoded NUTS units 1995-2021
  filter(typology== "country") %>% 
  select(typology, code_2016, geo_name_2016) %>%
  drop_na()

library(stringr)  # command str_sub()

## Nuts 2
eu_region_2$rob1 <- str_sub(eu_region_2$code_2016, 3, 4) #auxiliary variable to remove Extra-regions
eu_region_2$rob2 <- str_sub(eu_region_2$code_2016, 1, 2) #auxiliary variable to remove UK regions

eu_region_2 <- eu_region_2  %>%   #filtering regions
  filter(!rob1 == "ZZ") %>%              #remove extra region
  filter(!rob2 == "UK") %>%              #remove UK
  filter(!code_2016 %in% c("FRY1", "FRY2", "FRY3", "FRY4", "FRY5")) %>%  #remove French overseas regions
  mutate(geo = code_2016) %>%
  select(geo)

## Nuts 0
eu_region_0$rob1 <- str_sub(eu_region_0$code_2016, 3, 4) #auxiliary variable to remove Extra-regions
eu_region_0$rob2 <- str_sub(eu_region_0$code_2016, 1, 2) #auxiliary variable to remove UK regions

eu_region_0 <- eu_region_0  %>%   #filtering regions
  filter(!rob1 == "ZZ") %>%              #remove extra region
  filter(!rob2 == "UK") %>%              #remove UK
  filter(!code_2016 %in% c("FRY1", "FRY2", "FRY3", "FRY4", "FRY5")) %>%  #remove French overseas regions
  mutate(geo = code_2016) %>%
  select(geo)

unique(eu_region_0)
unique(eu_region_2)

```
```{r}
# NUTS 0
# inactivity rate 2019 Females 25-54 NUTS 0
inactivity_rate_eu_2019_F_0 <- inner_join(inactivity_rate_eu, eu_region_0) %>%  #merge the preliminary data frame with selected regions 
  filter(age == "Y25-54") %>%
  filter(sex == "F") %>%
  filter(time== 2019) %>%
  filter(edu!="edu_total") %>%
  filter(edu!="NRP") %>%
  filter(citizen=="TOTAL") %>%
  select(geo, edu, time, values)

# inactivity rate 2020 Females 25-54 NUTS 0
inactivity_rate_eu_2020_F_0 <- inner_join(inactivity_rate_eu, eu_region_0) %>%  #merge the preliminary data frame with selected regions 
  filter(age == "Y25-54") %>%
  filter(sex == "F") %>%
  filter(edu!="edu_total") %>%
  filter(time== 2020) %>%
  filter(edu!="NRP") %>%
  filter(citizen=="TOTAL") %>%
  select(geo, edu, time, values)

# inactivity rate 2021 Females 25-54 NUTS 0
inactivity_rate_eu_2021_F_0 <- inner_join(inactivity_rate_eu, eu_region_0) %>%  #merge the preliminary data frame with selected regions 
  filter(age == "Y25-54") %>%
  filter(sex == "F") %>%
  filter(edu!="edu_total") %>%
  filter(edu!="NRP") %>%
  filter(citizen=="TOTAL") %>%
  filter(time== 2021) %>%
  select(geo, edu, time, values)

```
```{r}
# NUTS 2
# inactivity rate 2019 Females 25-54 NUTS 2
inactivity_rate_eu_2019_F_2 <- inner_join(inactivity_rate_eu, eu_region_2) %>%  #merge the preliminary data frame with selected regions 
  filter(age == "Y25-54") %>%
  filter(sex == "F") %>%
  filter(time== 2019) %>%
  filter(edu!="edu_total") %>%
  filter(edu!="NRP") %>%
  filter(citizen=="TOTAL") %>%
  select(geo, edu, time, values)

# inactivity rate 2020 Females 25-54 NUTS 2
inactivity_rate_eu_2020_F_2 <- inner_join(inactivity_rate_eu, eu_region_2) %>%  #merge the preliminary data frame with selected regions 
  filter(age == "Y25-54") %>%
  filter(sex == "F") %>%
  filter(time== 2020) %>%
  filter(edu!="edu_total") %>%
  filter(edu!="NRP") %>%
  filter(citizen=="TOTAL") %>%
  select(geo, edu, time, values)

# inactivity rate 2021 Females 25-54 NUTS 0
inactivity_rate_eu_2021_F_2 <- inner_join(inactivity_rate_eu, eu_region_2) %>%  #merge the preliminary data frame with selected regions 
  filter(age == "Y25-54") %>%
  filter(sex == "F") %>%
  filter(time== 2021) %>%
  filter(edu!="edu_total") %>%
  filter(edu!="NRP") %>%
  filter(citizen=="TOTAL") %>%
  select(geo, edu, time, values)
```
```{r}
library(VIM)
mice_plot_1 <- aggr(inactivity_rate_eu_2019_F_0, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(inactivity_rate_eu_2019_F_0), cex.axis=.7,
                    gap=3, ylab=c("Missing data for inactivity rate eu 2019 F (25-54)","Pattern"))


```

```{r}
mice_plot_2 <- aggr(inactivity_rate_eu_2020_F_0, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(inactivity_rate_eu_2020_F_0), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
```

```{r}
mice_plot_3 <- aggr(inactivity_rate_eu_2021_F_0, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(inactivity_rate_eu_2021_F_0), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
```

```{r}
mice_plot_4 <- aggr(inactivity_rate_eu_2019_F_2, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(inactivity_rate_eu_2019_F_2), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
```

```{r}
mice_plot_5 <- aggr(inactivity_rate_eu_2020_F_2, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(inactivity_rate_eu_2020_F_2), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
```

```{r}
mice_plot_6 <- aggr(inactivity_rate_eu_2021_F_2, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(inactivity_rate_eu_2021_F_2), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
```
```{r}
#The NUTS 0 do not have missing values.
#The NUTS 2 data, have missing values. On the Values Column
# install.packages("mice")
library(mice)
summary(inactivity_rate_eu_2019_F_2)
# using the pmm algorithm (predictive mean matching)
my_imp_1 = mice(inactivity_rate_eu_2019_F_2, m=5, method = c("", "", "", "pmm"),maxit = 20)
my_imp_1$imp$values
# the 3rd iteration is chosen, due to it's closeness to the mean
inactivity_rate_eu_2019_F_2 = complete(my_imp_1,5)
summary(inactivity_rate_eu_2019_F_2)
```
```{r}
#For 2020 NUTS 2
summary(inactivity_rate_eu_2020_F_2)
# using the pmm algorithm (predictive mean matching)
my_imp_2 = mice(inactivity_rate_eu_2020_F_2, m=5, method = c("", "", "", "pmm"),maxit = 20)
my_imp_2$imp$values
# the 3rd iteration is chosen, due to it's closeness to the mean
inactivity_rate_eu_2020_F_2 = complete(my_imp_2,3)
summary(inactivity_rate_eu_2020_F_2) 

```
```{r}
# For 2021 NUTS 2
summary(inactivity_rate_eu_2021_F_2)
# using the pmm algorithm (predictive mean matching)
my_imp_3 = mice(inactivity_rate_eu_2021_F_2, m=5, method = c("", "", "", "pmm"),maxit = 20)
my_imp_3$imp$values
# the 2nd iteration is chosen, due to it's closeness to the mean
inactivity_rate_eu_2021_F_2 = complete(my_imp_3,2)
summary(inactivity_rate_eu_2021_F_2) 

```


```{r}
# b. Identify Outliers
#install.packages("rstatix")
library("rstatix")

inactivity_rate_eu_2019_F_0 %>%identify_outliers(values) 
inactivity_rate_eu_2020_F_0 %>%identify_outliers(values)
inactivity_rate_eu_2021_F_0 %>%identify_outliers(values)
inactivity_rate_eu_2019_F_2 %>%identify_outliers(values) 
inactivity_rate_eu_2020_F_2 %>%identify_outliers(values)
inactivity_rate_eu_2021_F_2 %>%identify_outliers(values)
```

```{r}
# c. Calculate mean values, standard deviation, max and min, range
min(inactivity_rate_eu_2019_F_0$values)
max(inactivity_rate_eu_2019_F_0$values)

dat <- list(inactivity_rate_eu_2019_F_0, inactivity_rate_eu_2020_F_0, inactivity_rate_eu_2021_F_0, inactivity_rate_eu_2019_F_2, inactivity_rate_eu_2020_F_2, inactivity_rate_eu_2021_F_2)

# Defining an empty dataframe

df = data.frame()

# Defining a for loop

for (i in dat) {
    
    output = c(mean(i$values),sd(i$values),min(i$values), max(i$values), range(i$values))
    
    # Using rbind() to append the output of one iteration to the dataframe
    df = rbind(df, output)
}

# naming the columns
colnames(df)<-c("mean", "Standard Dev", "min", "max", "range least", "range end")
row.names(df) <- c("2019 nuts 0", "2020 nuts 0", "2021 nuts 0", "2019 nuts 2", "2020 nuts 2", "2021 nuts 2")

# printing the dataframe
df

```

```{r}
# d. Present the data using boxplot
library(ggplot2)
level_orderX <- c("edu_low", "edu_medium","edu_high")   #order of the variable on the figure

# 2019 NUTS 0
ggplot(inactivity_rate_eu_2019_F_0, aes(x = factor(edu, level=level_orderX), y = values, fill=edu)) + 
  xlab("Level of education") + ylab("inactivity Rate")+
  stat_boxplot(geom = "errorbar",
              order = c("edu_low", "edu_medium", "edu_high"),
               width = 0.25) + 
  geom_boxplot(alpha = 0.8,          # Fill transparency
           colour = "#474747",       # Border color
           outlier.colour = 1) +
guides(fill = guide_legend(title = "NUTS 0 EU Females inactivity Rate in 2019 25-54"))

# 2020 Nuts 0
ggplot(inactivity_rate_eu_2020_F_0, aes(x = factor(edu, level=level_orderX), y = values, fill=edu)) + 
  xlab("Level of education") + ylab("inactivity Rate")+
  stat_boxplot(geom = "errorbar",
              order = c("edu_low", "edu_medium", "edu_high"),
               width = 0.25) + 
  geom_boxplot(alpha = 0.8,          # Fill transparency
           colour = "#474747",       # Border color
           outlier.colour = 1) +
guides(fill = guide_legend(title = "NUTS 0 EU Females inactivity Rate in 2020 25-54"))

# 2021 Nuts 0
ggplot(inactivity_rate_eu_2021_F_0, aes(x = factor(edu, level=level_orderX), y = values, fill=edu)) + 
  xlab("Level of education") + ylab("inactivity Rate")+
  stat_boxplot(geom = "errorbar",
              order = c("edu_low", "edu_medium", "edu_high"),
               width = 0.25) + 
  geom_boxplot(alpha = 0.8,          # Fill transparency
           colour = "#474747",       # Border color
           outlier.colour = 1) +
guides(fill = guide_legend(title = "NUTS 0 EU Females inactivity Rate in 2021 25-54"))


# 2019 NUTS 2
ggplot(inactivity_rate_eu_2019_F_2, aes(x = factor(edu, level=level_orderX), y = values, fill=edu)) + 
  xlab("Level of education") + ylab("inactivity Rate")+
  stat_boxplot(geom = "errorbar",
              order = c("edu_low", "edu_medium", "edu_high"),
               width = 0.25) + 
  geom_boxplot(alpha = 0.8,          # Fill transparency
           colour = "#474747",       # Border color
           outlier.colour = 1) +
guides(fill = guide_legend(title = "NUTS 2 EU Females inactivity Rate in 2019 25-54"))

# 2020 Nuts 2
ggplot(inactivity_rate_eu_2020_F_2, aes(x = factor(edu, level=level_orderX), y = values, fill=edu)) + 
  xlab("Level of education") + ylab("inactivity Rate")+
  stat_boxplot(geom = "errorbar",
              order = c("edu_low", "edu_medium", "edu_high"),
               width = 0.25) + 
  geom_boxplot(alpha = 0.8,          # Fill transparency
           colour = "#474747",       # Border color
           outlier.colour = 1) +
guides(fill = guide_legend(title = "NUTS 2 EU Females inactivity Rate in 2020 25-54"))

# 2021 Nuts 0
ggplot(inactivity_rate_eu_2021_F_2, aes(x = factor(edu, level=level_orderX), y = values, fill=edu)) + 
  xlab("Level of education") + ylab("inactivity Rate")+
  stat_boxplot(geom = "errorbar",
              order = c("edu_low", "edu_medium", "edu_high"),
               width = 0.25) + 
  geom_boxplot(alpha = 0.8,          # Fill transparency
           colour = "#474747",       # Border color
           outlier.colour = 1) +
guides(fill = guide_legend(title = "NUTS 2 EU Females inactivity Rate in 2021 25-54"))


```
```{r}
# removing the outliers and recalculating the mean
```


```{r}
library(tidyverse)
library(eurostat)
library(leaflet)
library(sf)
library(scales)
library(cowplot)
library(ggthemes)

get_eurostat_geospatial(resolution = 10, 
                        nuts_level = 0, 
                        year = 2016)

EU27 <- eu_countries %>% 
  filter(code != 'UK') %>% 
  select(geo = code, name)
SHP_0 <- get_eurostat_geospatial(resolution = 10, 
                                 nuts_level = 0, 
                                 year = 2016)
SHP_27 <- SHP_0 %>% 
  select(geo = NUTS_ID, geometry) %>% 
  inner_join(EU27, by = "geo") %>% 
  arrange(geo) %>% 
  st_as_sf()



tec00115_shp <- inactivity_rate_eu_2019_F_0 %>% 
  select(geo, values) %>% 
  inner_join(SHP_27, by = "geo") %>% 
  st_as_sf()

tec00115_shp %>% 
  ggplot(aes(fill = values)) +
  geom_sf(
    size = 0.1, 
    color = "#F3F3F3"
  ) +
  scale_fill_gradient2_tableau(
    palette = "Temperature Diverging",
    name = "%",
    breaks = pretty_breaks(10),
    guide = guide_colorbar(
      direction = "vertical", 
      title.position = "top", 
      label.position = "right",  
      barwidth = unit(0.4, "cm"), 
      barheight = unit(7, "cm"),  
      ticks = TRUE, 
    )
  ) + 
  scale_x_continuous(limits = c(-10, 35)) +
  scale_y_continuous(limits = c(35, 65)) +
  labs(
    title = "inactivity Rate Plot of EU Females aged 25-54 @NUTS 0",
    subtitle = "inactivity Rate in 2019",
    caption = "Data: Eurostat lfst_r_lfp2actrtn"
  ) +
  theme_void() +
  theme(legend.position = c(0.97, 0.50))
```
```{r}
library(tidyverse)
library(eurostat)
library(leaflet)
library(sf)
library(scales)
library(cowplot)
library(ggthemes)

get_eurostat_geospatial(resolution = 10, 
                        nuts_level = 0, 
                        year = 2016)

EU27 <- eu_countries %>% 
  filter(code != 'UK') %>% 
  select(geo = code, name)
SHP_0 <- get_eurostat_geospatial(resolution = 10, 
                                 nuts_level = 0, 
                                 year = 2016)
SHP_27 <- SHP_0 %>% 
  select(geo = NUTS_ID, geometry) %>% 
  inner_join(EU27, by = "geo") %>% 
  arrange(geo) %>% 
  st_as_sf()



tec00115_shp <- inactivity_rate_eu_2020_F_0 %>% 
  select(geo, values) %>% 
  inner_join(SHP_27, by = "geo") %>% 
  st_as_sf()

tec00115_shp %>% 
  ggplot(aes(fill = values)) +
  geom_sf(
    size = 0.1, 
    color = "#F3F3F3"
  ) +
  scale_fill_gradient2_tableau(
    palette = "Temperature Diverging",
    name = "%",
    breaks = pretty_breaks(10),
    guide = guide_colorbar(
      direction = "vertical", 
      title.position = "top", 
      label.position = "right",  
      barwidth = unit(0.4, "cm"), 
      barheight = unit(7, "cm"),  
      ticks = TRUE, 
    )
  ) + 
  scale_x_continuous(limits = c(-10, 35)) +
  scale_y_continuous(limits = c(35, 65)) +
  labs(
    title = "inactivity Rate Plot of EU Females aged 25-54 @NUTS 0",
    subtitle = "inactivity Rate in 2020",
    caption = "Data: Eurostat lfst_r_lfp2actrtn"
  ) +
  theme_void() +
  theme(legend.position = c(0.97, 0.50))
```

```{r}
library(tidyverse)
library(eurostat)
library(leaflet)
library(sf)
library(scales)
library(cowplot)
library(ggthemes)

get_eurostat_geospatial(resolution = 10, 
                        nuts_level = 0, 
                        year = 2016)

EU27 <- eu_countries %>% 
  filter(code != 'UK') %>% 
  select(geo = code, name)
SHP_0 <- get_eurostat_geospatial(resolution = 10, 
                                 nuts_level = 0, 
                                 year = 2016)
SHP_27 <- SHP_0 %>% 
  select(geo = NUTS_ID, geometry) %>% 
  inner_join(EU27, by = "geo") %>% 
  arrange(geo) %>% 
  st_as_sf()



tec00115_shp <- inactivity_rate_eu_2021_F_0 %>% 
  select(geo, values) %>% 
  inner_join(SHP_27, by = "geo") %>% 
  st_as_sf()

tec00115_shp %>% 
  ggplot(aes(fill = values)) +
  geom_sf(
    size = 0.1, 
    color = "#F3F3F3"
  ) +
  scale_fill_gradient2_tableau(
    palette = "Temperature Diverging",
    name = "%",
    breaks = pretty_breaks(10),
    guide = guide_colorbar(
      direction = "vertical", 
      title.position = "top", 
      label.position = "right",  
      barwidth = unit(0.4, "cm"), 
      barheight = unit(7, "cm"),  
      ticks = TRUE, 
    )
  ) + 
  scale_x_continuous(limits = c(-10, 35)) +
  scale_y_continuous(limits = c(35, 65)) +
  labs(
    title = "inactivity Rate Plot of EU Females aged 25-54 @NUTS 0",
    subtitle = "inactivity Rate in 2021",
    caption = "Data: Eurostat lfst_r_lfp2actrtn"
  ) +
  theme_void() +
  theme(legend.position = c(0.97, 0.50))
```
```{r}
library(tidyverse)
library(eurostat)
library(leaflet)
library(sf)
library(scales)
library(cowplot)
library(ggthemes)

SHP_2_3035  <- get_eurostat_geospatial(
  resolution = 10,
  nuts_level = 2,
  year = 2016,
  crs = 3035)

edat_lfse_04_shp <- inactivity_rate_eu_2019_F_2 %>% 
  right_join(SHP_2_3035, by = "geo") %>% 
  st_as_sf()
edat_lfse_04_shp %>% 
  ggplot(aes(fill = values)) +
  geom_sf(
    size = 0.1, 
    color = "#333333"
  ) +
  scale_fill_distiller(
    palette = "YlGnBu",
    direction = 1, 
    name = "%",
    breaks = pretty_breaks(10),
    na.value = "gray80",
    guide = guide_colorbar(
      direction = "vertical", 
      title.position = "top", 
      label.position = "right",  
      barwidth = unit(0.4, "cm"), 
      barheight = unit(6, "cm"),  
      ticks = TRUE, 
    )
  ) + 
  scale_x_continuous(limits = c(2500000, 7000000)) +
  scale_y_continuous(limits = c(1600000, 5200000)) +
  labs(
    title = "inactivity Rate Plot of EU Females aged 25-54 @NUTS 2",
    subtitle = "inactivity rate in 2019",
    caption = "Data: Eurostat lfst_r_lfp2actrtn"
  ) +
  theme_void() +
  theme(legend.position = c(0.94, 0.70))
```
```{r}
library(tidyverse)
library(eurostat)
library(leaflet)
library(sf)
library(scales)
library(cowplot)
library(ggthemes)

SHP_2_3035  <- get_eurostat_geospatial(
  resolution = 10,
  nuts_level = 2,
  year = 2016,
  crs = 3035)

edat_lfse_04_shp <- inactivity_rate_eu_2020_F_2 %>% 
  right_join(SHP_2_3035, by = "geo") %>% 
  st_as_sf()
edat_lfse_04_shp %>% 
  ggplot(aes(fill = values)) +
  geom_sf(
    size = 0.1, 
    color = "#333333"
  ) +
  scale_fill_distiller(
    palette = "YlGnBu",
    direction = 1, 
    name = "%",
    breaks = pretty_breaks(10),
    na.value = "gray80",
    guide = guide_colorbar(
      direction = "vertical", 
      title.position = "top", 
      label.position = "right",  
      barwidth = unit(0.4, "cm"), 
      barheight = unit(6, "cm"),  
      ticks = TRUE, 
    )
  ) + 
  scale_x_continuous(limits = c(2500000, 7000000)) +
  scale_y_continuous(limits = c(1600000, 5200000)) +
  labs(
    title = "inactivity Rate Plot of EU Females aged 25-54 @NUTS 2",
    subtitle = "inactivity rate in 2020",
    caption = "Data: Eurostat lfst_r_lfp2actrtn"
  ) +
  theme_void() +
  theme(legend.position = c(0.94, 0.70))
```

```{r}
library(tidyverse)
library(eurostat)
library(leaflet)
library(sf)
library(scales)
library(cowplot)
library(ggthemes)

SHP_2_3035  <- get_eurostat_geospatial(
  resolution = 10,
  nuts_level = 2,
  year = 2016,
  crs = 3035)

edat_lfse_04_shp <- inactivity_rate_eu_2021_F_2 %>% 
  right_join(SHP_2_3035, by = "geo") %>% 
  st_as_sf()
edat_lfse_04_shp %>% 
  ggplot(aes(fill = values)) +
  geom_sf(
    size = 0.1, 
    color = "#333333"
  ) +
  scale_fill_distiller(
    palette = "YlGnBu",
    direction = 1, 
    name = "%",
    breaks = pretty_breaks(10),
    na.value = "gray80",
    guide = guide_colorbar(
      direction = "vertical", 
      title.position = "top", 
      label.position = "right",  
      barwidth = unit(0.4, "cm"), 
      barheight = unit(6, "cm"),  
      ticks = TRUE, 
    )
  ) + 
  scale_x_continuous(limits = c(2500000, 7000000)) +
  scale_y_continuous(limits = c(1600000, 5200000)) +
  labs(
    title = "inactivity Rate Plot of EU Females aged 25-54 @NUTS 2",
    subtitle = "inactivity rate in 2021",
    caption = "Data: Eurostat lfst_r_lfp2actrtn"
  ) +
  theme_void() +
  theme(legend.position = c(0.94, 0.70))
```
```{r}
# Step 6: ANOVA analysis
# a
## Edu vs Values

## 1. 2019 @ NUTS 0 Level.
#Normality Test
shapiro.test(inactivity_rate_eu_2019_F_0$values)
shapiro.test(inactivity_rate_eu_2020_F_0$values)
shapiro.test(inactivity_rate_eu_2021_F_0$values)
shapiro.test(inactivity_rate_eu_2019_F_2$values)
shapiro.test(inactivity_rate_eu_2020_F_2$values)
shapiro.test(inactivity_rate_eu_2021_F_2$values)

anova_list <- list(inactivity_rate_eu_2019_F_0, inactivity_rate_eu_2020_F_0, inactivity_rate_eu_2021_F_0, inactivity_rate_eu_2019_F_2, inactivity_rate_eu_2020_F_2, inactivity_rate_eu_2020_F_2)

# All the p values are insignificant, hence the null hypothesis is rejected. All the data sets are not Normally distributed. Non-Parametric tests will be used.

```
```{r}
# Non Parametric Anova Analysis
#  Kruskal-Wallis rank sum test       

# Ordered Variaables for edu
inactivity_rate_eu_2019_F_0$edu <- ordered(inactivity_rate_eu_2019_F_0$edu,levels = c("edu_low", "edu_medium", "edu_high"))
inactivity_rate_eu_2020_F_0$edu <- ordered(inactivity_rate_eu_2020_F_0$edu,levels = c("edu_low", "edu_medium", "edu_high"))
inactivity_rate_eu_2021_F_0$edu <- ordered(inactivity_rate_eu_2021_F_0$edu,levels = c("edu_low", "edu_medium", "edu_high"))
inactivity_rate_eu_2019_F_2$edu <- ordered(inactivity_rate_eu_2019_F_2$edu,levels = c("edu_low", "edu_medium", "edu_high"))
inactivity_rate_eu_2020_F_2$edu <- ordered(inactivity_rate_eu_2020_F_2$edu,levels = c("edu_low", "edu_medium", "edu_high"))
inactivity_rate_eu_2021_F_2$edu <- ordered(inactivity_rate_eu_2021_F_2$edu,levels = c("edu_low", "edu_medium", "edu_high"))

#kruskal.test(edu~values, data = inactivity_rate_eu_2019_F_0)
anova_list <- list(inactivity_rate_eu_2019_F_0, inactivity_rate_eu_2020_F_0, inactivity_rate_eu_2021_F_0, inactivity_rate_eu_2019_F_2, inactivity_rate_eu_2020_F_2, inactivity_rate_eu_2020_F_2)

for (x in anova_list) {
    z<- kruskal.test(values~edu, data = x)
    print(z)
}

# As the p-values for NUTS 0 are greater than the significance level 0.05, we can conclude that there are no significant differences between the educational level and rate of inactivity.
# H0: The Educational Level does not affect the inactivity Rate. (The Educational Levels have the same distribution)
# H1: The Educational Level affects the inactivity rate. (The Educational Levels do not have the same distribution)
```

```{r}
# Post hoc Anova Test
# Dunn Test
library(FSA)

# Dunn's Test Data Prep

for (x in anova_list) {
    z<- dunnTest(x$values, x$edu, method = "bonferroni")
    print(z)
}
```

```{r}
# b. Across the Years

# Merging the Data Sets for NUTS 0 inactivity_rate_eu_F_0 = inactivity_rate_eu_2019_F_0 + inactivity_rate_eu_2020_F_0 + inactivity_rate_eu_2021_F_0
inactivity_rate_eu_F_0 <- do.call("rbind", list(inactivity_rate_eu_2019_F_0, inactivity_rate_eu_2020_F_0, inactivity_rate_eu_2021_F_0))

# High Education NUTS 0
inactivity_rate_eu_F_0_high <- inactivity_rate_eu_F_0 %>%
  filter(edu=="edu_high") %>%
  select(geo, edu, time, values)

# Medium Education NUTS 0
inactivity_rate_eu_F_0_medium <- inactivity_rate_eu_F_0 %>%
  filter(edu=="edu_medium") %>%
  select(geo, edu, time, values)

# Low Education NUTS 0
inactivity_rate_eu_F_0_low <- inactivity_rate_eu_F_0 %>%
  filter(edu=="edu_low") %>%
  select(geo, edu, time, values)

```


```{r}
# Merging the Data Sets for NUTS 2 inactivity_rate_eu_F_2 = inactivity_rate_eu_2019_F_2 + inactivity_rate_eu_2020_F_2 + inactivity_rate_eu_2021_F_2
inactivity_rate_eu_F_2 <- do.call("rbind", list(inactivity_rate_eu_2019_F_2, inactivity_rate_eu_2020_F_2, inactivity_rate_eu_2021_F_2))

# High Education NUTS 2
inactivity_rate_eu_F_2_high <- inactivity_rate_eu_F_2 %>%
  filter(edu=="edu_high") %>%
  select(geo, edu, time, values)

# Medium Education NUTS 2
inactivity_rate_eu_F_2_medium <- inactivity_rate_eu_F_2 %>%
  filter(edu=="edu_medium") %>%
  select(geo, edu, time, values)

# Low Education NUTS 2
inactivity_rate_eu_F_2_low <- inactivity_rate_eu_F_2 %>%
  filter(edu=="edu_low") %>%
  select(geo, edu, time, values)

```

```{r}
#Normality Test
shapiro.test(inactivity_rate_eu_F_0_high$values)
shapiro.test(inactivity_rate_eu_F_0_medium$values)
shapiro.test(inactivity_rate_eu_F_0_low$values)
shapiro.test(inactivity_rate_eu_F_2_high$values)
shapiro.test(inactivity_rate_eu_F_2_medium$values)
shapiro.test(inactivity_rate_eu_F_2_low$values)

```

```{r}
# Non Parametric Anova Analysis
#  Kruskal-Wallis rank sum test       

# Ordered Variaables for edu

#kruskal.test(edu~values, data = inactivity_rate_eu_2019_F_0)
anova_list_2 <- list(inactivity_rate_eu_F_0_high, inactivity_rate_eu_F_0_medium, inactivity_rate_eu_F_0_low, inactivity_rate_eu_F_2_high, inactivity_rate_eu_F_2_medium, inactivity_rate_eu_F_2_low)

for (x in anova_list_2) {
    z<- kruskal.test(values~time, data = x)
    print(z)
}

# As the p-values for NUTS 0 are greater than the significance level 0.05, we can conclude that there are no significant differences between the educational level and rate of inactivity.
# H0: The time/year does not affect the inactivity Rate. (The time levels have the same distribution)
# H1: The time/year affects the inactivity rate. (The time Levels do not have the same distribution)

# The years/periods observed: 2019, 2020 and 2021 almost all have the same distribution on the activity rate (there is no significant difference in their effects on EU Female Activity Rate).
```

```{r}

# Dunn's Test for inactivity_rate_eu_F_2_high

inactivity_rate_eu_F_2_high$time <- ordered(inactivity_rate_eu_F_2_high$time,levels = c(2019, 2020, 2021))

dunnTest(inactivity_rate_eu_F_2_high$values, inactivity_rate_eu_F_2_high$time, method = "bonferroni")
```

